Do NBA Teams Avoid Trading within Their Own Division?

### 2023-08-07 Manuscript.qmd
Network movie suppressed

<!-- Manually wrap in distill HTML tags to get a proper caption. -->
<div class="figure">
```{r animation, echo=FALSE}
htmltools::tags$iframe(src = 'NBA_Trades.html', width = '80%', height = '600px')
```
<p class="caption">Video 1. **Dynamic Visualization of Annual Trade Networks** Note: Intra-division trades are highlighted in red. Node color and position indicates division. The upper-right menu allows the animation speed to be adjusted while visualizing the entire sequence, or the forward/back buttons at the bottom can be used to step-wise animate the visualization one annual slice (trade season) at a time.</p>
</div>

>>>>

```{r fig-network-movie, eval=FALSE}
#| fig-cap: "**Dynamic Visualization of Annual Trade Networks** Availabe in the online supplement. Note: Intra-division trades are highlighted in red. Node color and position indicates division. The upper-right menu allows the animation speed to be adjusted while visualizing the entire sequence, or the forward/back buttons at the bottom can be used to step-wise animate the visualization one annual slice (trade season) at a time."
if(knitr::is_html_output()) {
  cat("<div class='figure'>\n")
  htmltools::tags$iframe(src = 'NBA_Trades.html', width = '80%', height = '600px')
  cat('<p class="caption">Video 1. **Dynamic Visualization of Annual Trade Networks** Note: Intra-division trades are highlighted in red. Node color and position indicates division. The upper-right menu allows the animation speed to be adjusted while visualizing the entire sequence, or the forward/back buttons at the bottom can be used to step-wise animate the visualization one annual slice (trade season) at a time.</p>
</div>\n')
} else {
  knitr::include_graphics("movie-still.png")
}
```
